Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig A1: Caption

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
        \caption{
            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
            run for a typical massive galaxy in the sample. 
            All the shaded regions are masked out. 
            The three dash lines (red, inner one and two blue ones) around the target 
            at the center outlines the three radius we defined using the flux radius 
            of the target.  
            We increase the mask size for objects detected in different regions 
            separated by these apertures (which are outlined by solid, elliptical 
            apertures with different colors) using slightly different criteria.~~
            \textbf{Middle:}: The flux profile that is zoomed into the near-zero flux 
            range (top panel), and the curve-of-growth of the magnitude for the example
            massive galaxy.  
            To highlight the importance of correcting sky background, we show the profiles 
            using both images with (red, solid line) and without (black, dash line) 
            ad-hoc background correction. 
            On the top panel, besides the horizontal line that highlights the zero flux 
            level, we also show the uncertainty of the sky background estimate via 
            grey-shaded region.  
            On the bottom panel, two horizontal lines indicate the magnitudes 
            corresponding to total (solid) and half flux (dash) using the 
            background-corrected profile. ~~
            \textbf{Right:} compare the 1-D surface brightness profiles for the same 
            example galaxy extracted using different mask 
            (smaller masking region: red, dash line; larger masks: blue, dash line), 
            or different \texttt{Ellipse} settings
            (more aggressive pixel-clipping: cyan, dash line; 
             larger step in radius: green, dash line; 
             using mean flux along the isophote instead of median: purple, dash line)
            with the one using the default configuration (black, solid line).
            }
        \label{fig:ell_tech}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_tech}
        \caption{
            \textbf{Left:} Example of the object-mask built for the \texttt{Ellipse}
            run for a typical massive galaxy in the sample. 
            All the shaded regions are masked out. 
            The three dash lines (red, inner one and two blue ones) around the target 
            at the center outlines the three radius we defined using the flux radius 
            of the target.  
            We increase the mask size for objects detected in different regions 
            separated by these apertures (which are outlined by solid, elliptical 
            apertures with different colors) using slightly different criteria.~~
            \textbf{Middle:}: The zoom-in intensity profile around very low intensity 
            value (top panel), and the curve-of-growth of the enclosed magnitude 
            (bottom panel) of the example galaxy.  
            To highlight the importance of background correction, we show the profiles 
            using both images with (red, solid line) and without (black, dotted line) 
            background correction. 
            On the top panel, besides the horizontal line that highlights the zero flux 
            level, we also show the uncertainty of the sky background estimate using 
            the grey-shaded region.  
            On the bottom panel, two horizontal lines indicate the magnitudes 
            corresponding to total flux (solid) and flux within 100 kpc (dash).~~
            \textbf{Right:} compares the 1-D surface brightness profiles for the same 
            example galaxy using different masks 
            (smaller masking region: red, dash line; larger masks: blue, dash line), 
            or different \texttt{Ellipse} configurations
            (more aggressive pixel-clipping: cyan, dash line; 
             larger step in radius: green, dash line; 
             using mean flux along the isophote instead of median: purple, dash line)
            with the default one (black, solid line).
            }
        \label{fig:ell_tech}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%
